### 2014-01-10 manuscripts/dpp-msbayes/dpp-msbayes-tables.tex
Playing with empirical model table of dpp ms.
Working on empirical model table for dpp ms.

>>>>

    \addtolength{\tabcolsep}{-0.08cm}
    \rowcolors{2}{myGray}{}
    \caption{The models used to analyze the data from the 22 pairs of taxa from
        the Philippines ($\mathbf{M}$), and a subset of nine of those pairs
        from the Islands of Negros and Panay ($\mathbb{M}$).
        In addition to the $\popSampleSize{}{} - 1$ coalescent times, the
        \empModelDPPSimple has only a single \myTheta{} parameter for
        each taxon pair.
        The remaining $\mathbf{M}$ models have three \myTheta{}, two
        \bottleScalar{}{}, and one \bottleTime{} parameters.
        The distributions of divergence times are given in units of
        \globalcoalunit generations and millions of generations ago (MGA), the
        latter assuming a per-site rate of 1\e{-8} mutations per generation.
        The \npModelDPP model (and its \npModelDPPOrdered counterpart
        that samples over ordered divergence models) has only two
        \myTheta{} parameters (the descendant populations of each
        pair share the same \myTheta{} parameter, and there are no
        bottleneck parameters).}
    \begin{tabulary}{\textwidth}{ l L }
        Model & Priors \\
            \empModelOld & $\divTimeIndexVector \sim \priorOld$ \tb
                      $\divTime{} \sim U(0,34.64)$ \tb
                      $\divTime{} \sim U(0,17.3 \; MGA)$ \tb
                      $\ancestralTheta{} \sim U(0, 0.01)$ \tb
                      $\descendantTheta{1}{}, \descendantTheta{2}{} \sim
                            Beta(1, 1) \times 2 \times U(0, 0.01)$ \tb
                      $\bottleScalar{1}{} \sim U(0, 1)$ \tb
                      $\bottleScalar{2}{} \sim U(0, 1)$ \\[0.25em]
            \empModelUniform & $\divTimeIndexVector \sim \priorUniform$ \tb
                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} \sim Exp(200)$ \tb
                      $\descendantTheta{2}{} \sim Exp(200)$ \tb
                      $\bottleScalar{1}{} \sim Beta(5, 1)$ \tb
                      $\bottleScalar{2}{} \sim Beta(5, 1)$ \\[0.25em]
            \empModelDPP & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(1.5,18.1)}$ \tb
                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} \sim Exp(200)$ \tb
                      $\descendantTheta{2}{} \sim Exp(200)$ \tb
                      $\bottleScalar{1}{} \sim Beta(5, 1)$ \tb
                      $\bottleScalar{2}{} \sim Beta(5, 1)$ \tb \\
            \empModelDPPInform & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(1.5,18.1)}$ \tb
                      $\divTime{} \sim Exp(1/6)$ \tb
                      $\divTime{} \sim Exp(mean=3 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} \sim Exp(200)$ \tb
                      $\descendantTheta{2}{} \sim Exp(200)$ \tb
                      $\bottleScalar{1}{} \sim Beta(5, 1)$ \tb
                      $\bottleScalar{2}{} \sim Beta(5, 1)$ \tb \\
            \empModelDPPSimple & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(1.5,18.1)}$ \tb
                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} = \descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(200)$ \tb
                      $\bottleScalar{1}{} = \bottleScalar{2}{} = 1.0$ \\[0.25em]
            \npModelDPP & $\divTimeIndexVector \sim \priorDPP{\sim Gamma(1.5,5.0)}$ \tb
                      $\divTime{} \sim Exp(0.1)$ \tb
                      $\divTime{} \sim Exp(mean=5 \; MGA)$ \tb
                      $\ancestralTheta{} \sim Exp(200)$ \tb
                      $\descendantTheta{1}{} = \descendantTheta{2}{} \sim Exp(200)$ \tb
                      $\bottleScalar{1}{} = \bottleScalar{2}{} = 1.0$ \\[0.25em]
    \end{tabulary}
    \label{tabEmpiricalModels}
